Preventing runtime errors of Redis at compile time

### 2015-11-17 paper.tex
4.2 Functions on type-level dictionaries

\subsection{Datatype promotion}
Normally, at the term level, we could express data type of the dictionary with
\emph{type synonym} like this.

@@

@@

@@

The first instance of \mintinline{haskell}{And} could be subsumed
under the more general instance \mintinline{haskell}{And a b}.
But the closedness allows these instances to be resoluted in order, just like
how cases are resoluted in term-level functions. Also notice that how much
\mintinline{haskell}{And} resembles to it's term-level brother.

@@

\footnotetext{\mintinline{haskell}{ping} from Hedis is qualified with
\mintinline{haskell}{Hedis} to prevent function name clashing}
%
% \mintinline{haskell}{IMonad} \mintinline{haskell}{IMonad} takes three arguments: an intitial state \mintinline{haskell}{p}, a final
%  state, and computes a value of type a

>>>>

\subsection{Datatype promotion}
Normally, at the term level, we could express data type of the dictionary with
\emph{type synonym} like this.\footnotemark

@@

\footnotetext{\mintinline{haskell}{TypeRep} here represents term-level
representations of datatypes, available in \mintinline{haskell}{Data.Typeable}}

@@

\footnotetext{\mintinline{haskell}{ping} from Hedis is qualified with
\mintinline{haskell}{Hedis} to prevent function name clashing}

@@

The first instance of \mintinline{haskell}{And} could be subsumed
under the more general instance \mintinline{haskell}{And a b}.
But the closedness allows these instances to be resoluted in order, just like
how cases are resoluted in term-level functions. Also notice that how much
\mintinline{haskell}{And} resembles to it's term-level sibling.

\subsection{Functions on type-level dictionaries}

With closed type families, we could define functions on the type level.
Let's begin with dictionary lookup.

\begin{minted}[xleftmargin=1em]{haskell}
type family Get
    (xs :: [(Symbol, *)])   -- dictionary
    (s :: Symbol)           -- key
    :: * where              -- type

    Get (’(s, x) ’: xs) s = x
    Get (’(t, x) ’: xs) s = Get xs s
\end{minted}

Another benifit of closed type families is that type-level equality can be
expressed by unifying type variables with the same name.
\mintinline{haskell}{Get} takes two type arguments, a dictionary and a symbol.
If the key we are looking for unifies with the symbol of an entry, then
 \mintinline{haskell}{Get} returns the corresponding type, else it keeps
 searching down the rest of the dictionary.

\mintinline{haskell}{Get }\mintinline{text}{ '}\mintinline{haskell}{[ }
\mintinline{text}{'}\mintinline{haskell}{("A", Int) ] "A"} evaluates to
\mintinline{haskell}{Int}.

But \mintinline{haskell}{Get }
\mintinline{text}{'}\mintinline{haskell}{[ }
\mintinline{text}{'}\mintinline{haskell}{("A", Int) ] "B"} would get stuck.
That's because \mintinline{haskell}{Get} is a partial function on types,
 and these types are computed at compile-time. It wouldn't make
much sense for type checkers to crash and throw a "Non-exhaustive" error or
be non-terminating.

We could make \mintinline{haskell}{Get} total, as we would at the term level,
with \mintinline{haskell}{Maybe}.

\begin{minted}[xleftmargin=1em]{haskell}
type family Get
    (xs :: [(Symbol, *)])   -- dictionary
    (s :: Symbol)           -- key
    :: Maybe * where        -- type

    Get ’[]             s = Nothing
    Get (’(s, x) ’: xs) s = Just x
    Get (’(t, x) ’: xs) s = Get xs s
\end{minted}

Other dictionary-related functions are defined in a similar way.

\begin{minted}[xleftmargin=1em]{haskell}
-- inserts or updates an entry
type family Set
    (xs :: [(Symbol, *)])   -- old dictionary
    (s :: Symbol)           -- key
    (x :: *)                -- type
    :: [(Symbol, *)] where  -- new dictionary

    Set ’[]             s x = ’[ ’(s, x) ]
    Set (’(s, y) ’: xs) s x = (’(s, x) ’: xs)
    Set (’(t, y) ’: xs) s x =
        ’(t, y) ’: (Set xs s x)

-- removes an entry
type family Del
    (xs :: [(Symbol, *)])   -- old dictionary
    (s :: Symbol)           -- key
    :: [(Symbol, *)] where  -- new dictionary

    Del ’[] s             = ’[]
    Del (’(s, y) ’: xs) s = xs
    Del (’(t, y) ’: xs) s = ’(t, y) ’: (Del xs s)

-- membership
type family Member
    (xs :: [(Symbol, *)])   -- dictionary
    (s :: Symbol)           -- key
    :: Bool where           -- exists?

    Member ’[]             s = False
    Member (’(s, x) ’: xs) s = True
    Member (’(t, x) ’: xs) s = Member xs s
\end{minted}

\begin{minted}[xleftmargin=1em]{haskell}
type family Get
    (xs :: [(Symbol, *)])   -- dictionary
    (s :: Symbol)           -- key
    :: Maybe * where        -- type

    Get ’[]             s = Nothing
    Get (’(s, x) ’: xs) s = Just x
    Get (’(t, x) ’: xs) s = Get xs s
\end{minted}

% \begin{minted}[xleftmargin=1em]{haskell}
% Get '['("ha", Int)]
% \end{minted}

@@

%
% \mintinline{haskell}{IMonad} \mintinline{haskell}{IMonad} takes three arguments: an intitial state \mintinline{haskell}{p}, a final
%  state, and computes a value of type a
